The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex
Add GPU support section

 \author[*1]{Daniel Arndt}
 \affil[1]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   \texttt{arndtd@ornl.gov}}

@@

The new \texttt{parallel::fullydistributed::Triangulation} class targets this issue
by distributing also the coarse grid. Such
a triangulation can be created by providing to each process a \texttt{Triangulation\-De\-scrip\-tion::Description} struct, containing
(i) the relevant data to construct the local part of the coarse grid, (ii) the
translation of the local coarse-cell IDs to globally unique IDs, (iii) the hierarchy
of mesh refinement steps, and (iv) the owner of the cells on the active mesh level as well
as on the multigrid levels. For the current release, triangulations set up
this way cannot be adaptively refined after construction, though we plann to
improve this for the next release.

@@

\begin{itemize}
\item overlapping of computation and communication in the case of CUDA-aware MPI
\end{itemize}

@@

The initial support for Python has come in \texttt{deal.II 9.0}. The present release significantly extends the Python interface. Specficically, a large number of methods from the C++ classes such as \texttt{Triangulation, CellAccessor, TriaAccessor, Mapping, Manifold, GridTools} can now be invoked from within the Python. The accent was made on methods and functions that are widely used at a mesh preparation stage when a mesh is created and parameters related to the boundary, manifold and material identifiers are assigned.

>>>>

 \author[*1]{Daniel Arndt}
 \affil[1]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   \texttt{arndtd/turcksinbr@ornl.gov}}

@@

The new \texttt{parallel::fullydistributed::Triangulation} class targets this issue
by distributing also the coarse grid. Such
a triangulation can be created by providing to each process a \texttt{Triangulation\-De\-scrip\-tion::Description} struct, containing
(i) the relevant data to construct the local part of the coarse grid, (ii) the
translation of the local coarse-cell IDs to globally unique IDs, (iii) the hierarchy
of mesh refinement steps, and (iv) the owner of the cells on the active mesh level as well
as on the multigrid levels. For the current release, triangulations set up
this way cannot be adaptively refined after construction, though we plan to
improve this for the next release.

@@

For this release, the most noteworthy improvements for the GPU support are the
simplification of the kernel written by user, improvement of the error messages,
and overlapping of computation and communication when using CUDA-aware MPI with
the matrix-free framework. In order to simplify user code, we know recompute the
local degree of freedom and quadrature point indices instead of having the user
keeping track of them. A new option to overlap computation and communication is
now available when using CUDA-aware MPI and matrix-free. The underlying idea is
that only the degrees of freedom (dofs) on the boundary of the local domain
require communication. Before evaluating the matrix-free operator at these
degrees of freedom, we need to communicate the ghosted dofs from other
processors.  Similarly once the operator has been evaluated, we need to update
the resulting global vector with values from other processors. The strategy that
we are using consist in splitting the dofs in three groups: one group of dofs
that are on the local boundary and two groups each owning half of the interior
dofs. When evaluating the matrix-free operator, we start the MPI communication
to get the ghosted dofs and evaluate the operator on one of the two interior
dofs group. When the evaluation is done, we wait for the MPI to be over and
then, evaluate the operator on the boundary dofs group. When this evaluation is
over, we start the communication to update the global vector, we evaluate the
operator on the last of group of dofs, and finally wait for the MPI
communication to finish.

@@

The initial support for Python has come in \texttt{deal.II 9.0}. The present release significantly extends the Python interface. Specifically, a large number of methods from the C++ classes such as \texttt{Triangulation, CellAccessor, TriaAccessor, Mapping, Manifold, GridTools} can now be invoked from Python. The accent was made on methods and functions that are widely used at a mesh preparation stage when a mesh is created and parameters related to the boundary, manifold and material identifiers are assigned.
